Dual host-parasite transcriptomes of apicomplexan Eimeria falciformis and its natural mouse host

### 2016-08-15 manuscript/bmc_article.tex
A remider on the ortholog comparisons...

>>>>

\section*{Evolutionary conservation of expression changes in \textit{E. falciformis}}

For comparison of changes in the lifecycle of \textit{E. falciformis}
with the economically important chicken parasite \textit{E. tenella}
and the model apicompomplexan \textit{Toxoplasma gondii} we downloaded
expresson datasets from ...

Oocysts, Sproozoites
